### 2020-09-08 manuscript/manuscript.rmd
add two sentences of importance of heterogeneous

This dependence alone doesn't resolve the question of where the root falls in the animal tree of life, that depends on how we interpret this dependence. Focusing just on heterogeneous analyses of matrices with restricted outgroup sampling, should we believe the results with fewer equilibrium frequency categories or the results with many? Moreover, taxa sampling also plays an important role in this question since data matrices with more ctenophores (and outgroups) generally results in more support for Ctenophora-sister.

>>>>

This dependence alone doesn't resolve the question of where the root falls in the animal tree of life, that depends on how we interpret this dependence. Focusing just on heterogeneous analyses of matrices with restricted outgroup sampling, should we believe the results with fewer equilibrium frequency categories or the results with many? Moreover, taxa sampling also plays an important role in this question since data matrices with more ctenophores (and outgroups) generally results in more support for Ctenophora-sister. Importantly, we want to emphasize that our concern here is not with the heterogeneous analyses but with unrealistic large number of unconstrained substitutional categories. The heterogeneity is important to consider in future phylogenomic studies (especially for exploring the deep relationships), but the results should be carefully examined.
